### 2017-06-08 sheets/talk-6/sheet-6.tex

\begin{exercise}[Direct Sum of Vector Spaces]
  In the talk we have seen that the direct sum $V \oplus W$ of two vector spaces $V, W$ over a fixed field $K$ is the coproduct of $V$ and $W$.
  Show that it is also the product.
\end{exercise}

@@

\begin{definition}{Minus-Core of Linear Maps in Vector Spaces}
  Let $V, W$ be Vector Spaces over a field $K$. Let $s, t \from V \to W$ be linear functions.
  We define the linear function $s - t := \lambda v\in V. \; v(s) - t(s)$.
  Remember that for $g \from V \to W$ we have defined $core(g) := \set{ v \in V | g(v) = 0 }$.
  Now $core (s - t) = \set{v \in V | s(v) = t (v) }$.
\end{definition}

\begin{exercise}[Equalizer of Vector Spaces]
  Let
  $\xymatrix{
      X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
  }$
  be a diagramm in $Vect_K$ for a field $K$. Show that $core(s-t)$ is the equalizer for this diagramm.
\end{exercise}

@@

\begin{definition}{Reflexive,\ symmetric\ and transitive\ closure}
  Let $X$ be a arbitrary set and $R \subseteq X \times X$ a binary relation over $X$.
  We define $R_0 := R \cup \set{ (y, x) | (x, y) \in R} \cup \set{ (x, x) | x \in X}$,
  the the \emph{reflexive, symmetric closure} of R.
  Now we define inductively $\forall n \in \nat$:
  \[R_{n+1} := \set{(x_1, x_3) \in R \times R \; | \; \exists x_2 \in X, (x_1, x_2) \in R_n \land (x_2, x_3) \in R_n}.\]
  Now $S := \bigcup_{n \in \nat}{R_n}$ is the reflexive, symmetric and transitive closure of $R$.
\end{definition}

>>>>

\begin{exercise}[Direct sum of vector spaces]
  In the talk we have seen that the direct sum $V \oplus W$ of two vector spaces $V, W$ over a fixed field $K$ is the coproduct of $V$ and $W$.
  Show that it is also the product.
\end{exercise}

@@

\begin{definition}{Minus-core of linear maps in vector spaces}
  Let $V, W$ be vector spaces over a field $K$. Let $s, t \from V \to W$ be linear functions.
  We define the linear function $s - t := \lambda v\in V. \; v(s) - t(s)$.
  Remember that for $g \from V \to W$ we have defined $core(g) := \set{ v \in V | g(v) = 0 }$.
  Now $core (s - t) = \set{v \in V | s(v) = t (v) }$.
\end{definition}

\begin{exercise}[Equalizer of vector spaces]
  Let
  $\xymatrix{
      X \ar@<.5ex>[r]^s \ar@<-.5ex>[r]_t & Y
  }$
  be a diagramm in $Vect_K$ for a field $K$. Show that $core(s-t)$ is the equalizer for this diagramm.
\end{exercise}

@@
